---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# natverse <a href='https://natverse.github.io/'><img src='man/figures/logo.svg' align="right" height="138.5" /></a>

<!-- badges: start -->
[![natverse](https://img.shields.io/badge/natverse-Part%20of%20the%20natverse-a241b6)](https://natverse.github.io)
[![Docs](https://img.shields.io/badge/docs-100%25-brightgreen.svg)](https://natverse.github.io/natverse/reference/)
[![Travis build status](https://travis-ci.org/natverse/natverse.svg?branch=master)](https://travis-ci.org/natverse/natverse)
<!-- badges: end -->

The goal of natverse is to install all of the commonly used NeuroAnatomy Toolbox packages.

See https://natverse.github.io for more details.

## Installation

You can install the latest version of natverse using NatManager as shown below:

```r
if(!requireNamespace('remotes')) install.packages('remotes')
remotes::install_github("natverse/NatManager")
library(NatManager)
NatManager::install('natverse', dependencies = TRUE)
```

Once installed, you can update the elements of the natverse package and its dependencies like:

```r
natverse_update(update = TRUE)
```
This will ask you to confirm whether you want to update dependencies (and their dependencies).

However, if you are in a hurry and want to save time from the questions use like below:

```r
natverse_update(update=TRUE, upgrade = 'always')
```

If want to upgrade the natverse package itself:

```r
remotes::update_packages('natverse')
```

## Example

This will load the `natverse` package:

```{r example}
library(natverse)
```

Conflicts between functions added to the search path by loading the `natverse` and equivalently named functions in other packages can by running:

```{r conflicts}
natverse_conflicts()
```

You can check if all the packages within `natverse` are up to date with:

```{r check status}
natverse_deps()
```
