---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# natverse <a href='https://natverse.github.io/'><img src='man/figures/logo.svg' align="right" height="138.5" /></a>

<!-- badges: start -->
<!-- badges: end -->

The goal of natverse is to install all of the commonly used NeuroAnatomy Toolbox packages.

See https://jefferis.github.io/nat/ for more details.

## Installation

You can install the latest version as shown below:

``` r
# install.packages("devtools")
devtools::install_github("SridharJagannathan/natverse")
```
## Example

This will load the `natverse` package:

```{r example}
library(natverse)
```

The conflicts created by `natverse` with other packages can be seen with

```{r conflicts}
natverse_conflicts()
```

You can check if all the packages within `natverse` are uptodate with:

1.For dependencies installed via CRAN use

```{r updates_CRAN}
natverse_update(source = 'CRAN')
```
2.For dependencies installed via GitHub use
```{r updates_GitHub}
natverse_update(source = 'GITHUB')
```

