---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# natverse <a href='https://natverse.github.io/'><img src='man/figures/logo.svg' align="right" height="138.5" /></a>

<!-- badges: start -->
[![natverse](https://img.shields.io/badge/natverse-Part%20of%20the%20natverse-a241b6)](https://natverse.github.io)
[![GitHub](https://img.shields.io/github/v/release/natverse/natverse)](https://github.com/natverse/natverse/releases/)
[![Docs](https://img.shields.io/badge/docs-100%25-brightgreen.svg)](https://natverse.github.io/natverse/reference/)
[![Travis build status](https://travis-ci.org/natverse/natverse.svg?branch=master)](https://travis-ci.org/natverse/natverse)
[![Coveralls test coverage](https://coveralls.io/repos/github/natverse/natverse/badge.svg)](https://coveralls.io/r/natverse/natverse?branch=master)
<!-- badges: end -->

The natverse package is a wrapper for all of the commonly used NeuroAnatomy 
Toolbox packages. This is convenient both for package installation and
for loading/attaching these packages without many calls to `library()`.

See http://natverse.org for more details.

## Installation

The recommended approach to install the full natverse is to use a helper 
package natmanager, which is available on CRAN. You can therefore do:

```r
install.packages("natmanager")
natmanager::install("natverse")
```
See http://natverse.org/install for more details.

## Use
Once installed, you can load the `natverse` package:

```{r example}
library(natverse)
# example 3D plot of some neurons
plot(kcs20, col=type)
```


## Installation Details

### Conflicts and Dependencies

The natverse package contains many packages and it is possible that
there could be conflicts where functions in the natverse have the same
name as another package.

```{r conflicts}
natverse_conflicts()
```

You can always choose the correct version by prepending the specific
package name e.g. `nat::flip()` will select the nat version rather than any other.

### Updates
Once installed, you check the status of all natverse packages and 
their dependencies like so:

```{r}
natverse_update()
```

You can then update like so:

```{r, eval=FALSE}
natverse_update(update = TRUE)
```

However, if you are in a hurry and want to save time from the questions use like below:

```{r, eval=FALSE}
natverse_update(update=TRUE, upgrade = 'always')
```

If want to upgrade the natverse package itself:

```{r, eval=FALSE}
remotes::update_packages('natverse')
```

